---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CMPS

<!-- badges: start -->
<!-- badges: end -->

The goal of CMPS is to ...

## Installation

You can install the released version of CMPS from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("CMPS")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("willju-wangqian/CMPS")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(CMPS)
## basic example code
```

## preconsiderations folder

- `demo_get_ccf.Rmd` is a demo that compares `get_ccf()`, `get_ccf2()`, and `get_ccf3()`. And my suggestion on how we can modify and use `get_ccf()`

- `func_collection.R` has all functions I currently have

- `current_working.R` has codes that I'm working with right now, including `findpeaks()` and `sig_get_peaks()`

- `CMPS_basic.R` has codes that I started with, but it's not important at this point.

- `past_codes.R` serves as a backup for out-of-date codes
